### 2025-07-20 decision-making.qmd
20250719 - bracketing rate

```{r}
# insert example using historical projections: wisdomOfCrowd()

seasonalIndividualSources <- projectionsWithActuals_seasonal %>%
  filter(!is.na(raw_points)) %>% 
  filter(!is.na(fantasyPoints)) %>% 
  group_by(player_id, season) %>%
  filter(n() >= 2) %>% # at least 2 projections
  summarise(
    numProjections = n(),
    type = "individual",
    petersenlab::wisdomOfCrowd(
      predicted = raw_points,
      actual = unique(fantasyPoints),
      dropUndefined = TRUE
      )[1,],
    .groups = "drop"
  )

```{r}
#length()
```

@@

>>>>

@@

```{r}
seasonalIndividualSources <- projectionsWithActuals_seasonal %>%
  filter(!is.na(raw_points)) %>% 
  filter(!is.na(fantasyPoints)) %>% 
  group_by(player_id, season) %>%
  filter(n() >= 2) %>% # at least 2 projections
  summarise(
    numProjections = n(),
    type = "individual",
    petersenlab::wisdomOfCrowd(
      predicted = raw_points,
      actual = unique(fantasyPoints),
      dropUndefined = TRUE
      )[1,],
    .groups = "drop"
  )

```{r}
seasonalIndividualSources %>% 
  select(player_display_name, position, season, numProjections, bracketingRate, ME:RMSLE)
```

```{r}
seasonalIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n())
```

```{r}
weeklyIndividualSources <- projectionsWithActuals_weekly %>%
  filter(!is.na(raw_points)) %>% 
  filter(!is.na(fantasyPoints)) %>% 
  group_by(player_id, season, week) %>%
  filter(n() >= 2) %>% # at least 2 projections
  summarise(
    numProjections = n(),
    type = "individual",
    petersenlab::wisdomOfCrowd(
      predicted = raw_points,
      actual = unique(fantasyPoints),
      dropUndefined = TRUE
      )[1,],
    .groups = "drop"
  )

weeklyCrowd <- projectionsWithActuals_weekly %>%
  filter(!is.na(raw_points)) %>% 
  filter(!is.na(fantasyPoints)) %>% 
  group_by(player_id, season, week) %>%
  filter(n() >= 2) %>% # at least 2 projections
  summarise(
    numProjections = n(),
    type = "crowd",
    petersenlab::wisdomOfCrowd(
      predicted = raw_points,
      actual = unique(fantasyPoints), # [1] error w/o [1] because have more than one unique value for a given player-season-week
      dropUndefined = TRUE
      )[2,],
    .groups = "drop"
  )

weeklyIndividualSourcesAndCrowd <- bind_rows(
  weeklyIndividualSources,
  weeklyCrowd
)

weeklyIndividualSources <- weeklyIndividualSources %>% 
  left_join(
    player_stats_weekly,
    by = c("player_id", "season", "week")
  )

weeklyCrowd <- weeklyCrowd %>% 
  left_join(
    player_stats_weekly,
    by = c("player_id", "season", "week")
  )

weeklyIndividualSourcesAndCrowd <- weeklyIndividualSourcesAndCrowd %>% 
  left_join(
    player_stats_weekly,
    by = c("player_id", "season", "week")
  )
```

```{r}
weeklyIndividualSources %>% 
  select(player_display_name, position, season, week, numProjections, bracketingRate, ME:RMSLE)
```

```{r}
#| label: fig-bracketingRateWeekly
#| fig-cap: "Distribution of Bracketing Rate Across Players For Weekly Projections."
#| fig-alt: "Distribution of Bracketing Rate Across Players For Weekly Projections."

ggplot2::ggplot(
  data = weeklyIndividualSources %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = bracketingRate)
) +
  geom_histogram(
    color = "#000000",
    fill = "#0099F8"
  ) +
  labs(
    x = "Bracketing Rate",
    y = "Count",
    title = "Histogram of Bracketing Rate (Weekly Projections)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5))
```

```{r}
weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n())
```
